---
title: CV/Resume
output:
  html_document
theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(splitstackshape)

```

```{r}

CSV <- read_csv("data_CV.csv") %>%
  janitor::clean_names() %>%
  mutate(section = as.factor(section),
         subsection = as.factor(subsection),
         subsubsection = as.factor(subsubsection),
         category = as.factor(category)) %>% 
  group_by(section, subsection, subsubsection)

CSV2 <- pivot_wider(CSV, names_from = category, values_from = content) %>% 
  select(-entity, -title)

CSV_when <- as.data.frame(iconv(as.character(CSV2$when), from = "latin1", to = "ASCII", sub="-")) %>% ungroup() %>% droplevels()
names(CSV_when) <- "when"

CSV2 <- CSV2 %>%
  select(-when) %>% 
  cbind(CSV_when$when) %>% 
  droplevels()

```

# `r CSV$content[1]`

 `r CSV$content[2]` | `r CSV$content[3]` | `r CSV$content[4]` | `r CSV$content[5]`

## Education

### `r CSV2$with[6]`

`r CSV2$what[6]`

`r CSV2$...9[6]`

- GPA: `r CSV2$why[6][[1]][1]`

- Specialization: `r CSV2$why[6][[1]][2]`

- Foci: `r CSV2$why[6][[1]][3]` & Data Science


### `r CSV2$with[7]`

`r CSV2$what[7]`

`r CSV2$...9[7]`

- GPA: `r CSV2$why[7][[1]][2]`

- Concentration:  `r CSV2$why[7][[1]][3]`

- `r CSV2$why[7][[1]][4]`


### `r CSV2$with[8]`

`r CSV2$...9[8]`

- GPA: `r CSV2$why[8][[1]][2]`

- `r CSV2$why[8][[1]][1]`



## `r CSV$content[23]`

### `r CSV2$with[10]`

`r CSV2$what[10]`

`r CSV2$...9[10]`
`r CSV2$where[10]`

- `r CSV2$why[10][[1]][1]`

- `r CSV2$why[10][[1]][2]`


### `r CSV2$with[11]`

`r CSV2$what[11]`

`r CSV2$...9[11]`
`r CSV2$where[11]`

- `r CSV2$why[11][[1]][1]`

- `r CSV2$why[11][[1]][2]`


`r CSV2$what[12]`

`r CSV2$...9[12]`
`r CSV2$where[12]`

- `r CSV2$why[12][[1]][1]`

- `r CSV2$why[12][[1]][2]`


`r CSV2$what[13]`

`r CSV2$...9[13]`
`r CSV2$where[13]`

- `r CSV2$why[13][[1]][1]`


### `r CSV2$with[14]`

`r CSV2$what[14]`

`r CSV2$...9[14]`
`r CSV2$where[14]`

- `r CSV2$why[14][[1]][1]`

- `r CSV2$why[14][[1]][2]`

`r CSV2$what[15]`

`r CSV2$...9[15]`
`r CSV2$where[15]`

- `r CSV2$why[15][[1]][1]`

- `r CSV2$why[15][[1]][2]`

`r CSV2$what[16]`

`r CSV2$...9[16]`
`r CSV2$where[16]`

- `r CSV2$why[16][[1]][1]`

- `r CSV2$why[16][[1]][2]`


### `r CSV2$subsection[17]`



## `r CSV$content[67]`
### `r CSV$content[68]`
- `r CSV2$what[19][[1]][1]`
- `r CSV2$what[19][[1]][2]`
- `r CSV2$what[19][[1]][3]`
- `r CSV2$what[19][[1]][4]`
- `r CSV2$what[19][[1]][5]`
- `r CSV2$what[19][[1]][6]`
- `r CSV2$what[19][[1]][7]`
- `r CSV2$what[19][[1]][8]`
- `r CSV2$what[19][[1]][9]`

### `r CSV$content[78]`
- `r CSV2$what[20][[1]][1]`
- `r CSV2$what[20][[1]][2]`
- `r CSV2$what[20][[1]][3]`
- `r CSV2$what[20][[1]][4]`
- `r CSV2$what[20][[1]][5]`
- `r CSV2$what[20][[1]][6]`
- `r CSV2$what[20][[1]][7]`
- `r CSV2$what[20][[1]][8]`
- `r CSV2$what[20][[1]][9]`
- `r CSV2$what[20][[1]][10]`
- `r CSV2$what[20][[1]][11]`